Sr: Processing Data Streams By Doing Less Work

### 2012-05-03 paper/paper.tex
move some sections around

\section{Evaluation}
To evaluate Sr, I explore the speedup factor associated with varying the kill rate and target work level as well as the precision and recall of the word count test job.
\subsection{Speedup}
Sr is able to achieve a speedup over a MapReduce-style computation through three mechanisms: providing multiple computation routines for the workers to choose from; varying the task kill rate; and varying the target work level, which influences the chosen frequency of computation routines per worker.

Table ~\ref{table:runtime} shows the effect of varying the kill rate and work level. The row with kill rate = 0.0 and work level = 1.0 represents the perfect, “correct” execution of the word count job. The only consistent reduction in execution time is a result of increasing the kill rate. Increasing the kill rate exhibits a linear reduction in execution time as the fraction of processed data linearly decreases.

@@

\begin{figure}
\includegraphics[width=\linewidth]{long-tail-ranks.png}
\caption{Frequencies of words in the Wikipedia Featured Articles corpus}
\label{fig:wordDist}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\linewidth]{top-100-precision.png}
\caption{Precision of top 100 results} 
\label{fig:precision}
\end{figure}

\subsubsection{Test Accuracy}
Because I am running a top k job, I compute the $F_{0.5}$-score of the Sr results as opposed to the $F1$-score because I care more about precision of the top k than recall in the tail.

>>>>

\section{Evaluation}
To evaluate Sr, I explore the precision and recall of the word count test job as well as the speedup factor associated with varying the kill rate and target work level.

@@

\begin{figure}
\includegraphics[width=\linewidth]{long-tail-ranks.png}
\caption{The frequencies of words in the Wikipedia Featured Articles corpus have a long-tailed distribution.}
\label{fig:wordDist}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\linewidth]{top-100-precision.png}
\caption{Number of top 100 results returned in the top-100 by the word count job}
\label{fig:precision}
\end{figure}

\subsubsection{Word Count Job Accuracy}
Because I am running a top-k job, I compute the $F_{0.5}$-score of the Sr results as opposed to the $F1$-score because I care more about precision of the top k than recall in the tail. Figure ~\ref{fig:fscore} shows that the $F_{0.5}$-score, or the weighted accuracy of the top-100 classifier, is always higher than the fraction of the input examined (kill rate * work level).

\begin{figure}
\includegraphics[width=\linewidth]{f-score.png}
\caption{$F_{0.5}$-score for the top-100 word count job. I measured the $F$-score with $\beta = 0.5$ because the goal of the job is to run a top-k filter on it, meaning I care more about precision than recall.}
\label{fig:fscore}
\end{figure}

\subsection{Speedup}
Sr is able to achieve a speedup over a MapReduce-style computation through three mechanisms: providing multiple computation routines for the workers to choose from; varying the task kill rate; and varying the target work level, which influences the chosen frequency of computation routines per worker.

Table ~\ref{table:runtime} shows the effect of varying the kill rate and work level. The row with kill rate = 0.0 and work level = 1.0 represents the perfect, MapReduce-style, execution of the word count job. The only consistent reduction in execution time is a result of increasing the kill rate. Increasing the kill rate exhibits a linear reduction in execution time as the fraction of processed data linearly decreases.

Notably, simply by killing tasks, Sr is able to achieve over a 5 times speedup compared to the perfect execution while still returning about 84 of the top-100 words.
